---
title: "envs193ds_hw3"
author: "Hibah Ganie"
date: "2025-05-28"
output: html_document
---
## [Hibah's Github Repository](https://github.com/hibdawg/ENVS-193DS_homework-03)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Reading In Packages and Data}
library(tidyverse) # General Use
library(janitor) # Cleaning data Frames
library(dplyr) # Mutate columns
library(lubridate) # make dealing with dates easier
library(here) # File Organization
library(readxl) # reading .xlsx files
library(ggeffects) # generating model predictions
library(gtsummary) # generating summary tables for models 
library(ggplot2)
library(readr) # Reads in Data 

my_data <- read_csv(here("data", "hibdata2.csv")) # read in my data
```

```{r Cleaning My Data}
clean_hibdata <- my_data |> 
  clean_names() |> 
  select(time, scouting, finals_week, week, outlet, shared_table, duration, floor_level, dayw) |> 
  rename(exam_week = finals_week,
         shared = shared_table,
         floor = floor_level,
         day = dayw) |> 
  separate(duration, into = c("hours", "minutes"), sep = ":", convert = TRUE) |>
  mutate(
    total_minutes = hours * 60 + minutes,
    duration_category = if_else(total_minutes < 90, "short", "long")
  )
```


### Part 2. Problems
## Problem 1. Personal Data 

# Data Summarizing 
A. . I could compare how the duration of events follows my class schedule and see how I have shorter events on days where I have class due to gaps in my schedule where I study. I also want to compare how total study time based on weeks increase, or may taper off as I struggle to find a spot in the library and may need to go elsewhere to study. 

B. 
```{r Data Visualization}
ggplot(
  clean_hibdata, # Select Clean Datafram
  aes(x = day, # X axis
      fill = duration_category) # based on Category of Session Length
) +
  geom_bar(position = "dodge") + # Bar Graph
  labs( # Add labels
    title = "Short vs Long Sessions by Day", # title of Graph
    x = "Days of the Week", # X Label
    y = "Number of Sessions", # Y Lael
    fill = "session Length", # Differentiate Based on category
    caption = "y a mama."
  ) + 
  theme_classic() + # choose theme!
  scale_fill_manual( # mannually change colors 
    values = c("short" = "pink", # pink
               "long" = "orange")) # orange
```


